### 2022-02-09 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
reorganize Christine Chan's files

---
title: ""
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

>>>>

---
title: "Pre-/Post-Trikafta (Prospective)"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

### 2022-02-09 Colleen Wood/Pre-post Trikafta/pre_post_trikafta_merge.Rmd
reorganize Christine Chan's files

# continuous glucose monitoring, 23 obs
# 105 vars subjectid - number_pre/post for visit and a date; numbers dont seem to correspond to mrn in bmi pft
chco_cgm = read_csv("./Prepost Triakfta/Data_Cleaned/chco_cgm.csv")

# chco glycemic, 261 obs
# 7 var MRN and CFF id (=subjectid?), date for visits; start... etc
chco_glycemic = read_csv("./Prepost Triakfta/Data_Cleaned/chco_glycemic.csv")

>>>>

# continuous glucose monitoring, 23 obs
# 105 vars subjectid - number_pre/post for visit and a date; numbers dont seem to correspond to mrn in bmi pft
chco_cgm = read_csv("./Prepost Triakfta/Data_Cleaned/chco_cgm.csv")
chco_cgm$Date = lubridate::date(parse_date_time(chco_cgm$date_cgm_placement,
                                                orders = c("mdyHM","mdy")))
# chco glycemic, 261 obs
# 7 var MRN and CFF id (=subjectid?), date for visits; start... etc
chco_glycemic = read_csv("./Prepost Triakfta/Data_Cleaned/chco_glycemic.csv")
